---
title: "Indoor Track & Field Program Records"
author: "Georgetown College Track & Field"
date: "Updated:`r Sys.time()`"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    css: style.css
  pdf_document: default
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(DT)
require(rvest)
require(XML2)


scrpTFRRS <- function(url){

  scraped <- read_html(url)

  test1 <- scraped %>%
    html_nodes("table") %>%
    .[-1] %>%
    html_table(fill = TRUE)

  events <- html_nodes(scraped, '.custom-table-title')
  events_txt <- html_text(events)
  events_txt <- gsub("\n","",events_txt)
  events_txt <- gsub("\t","",events_txt)
  events_txt <- gsub(" ","",events_txt)

  names(test1)=events_txt
  return(test1)
}

listMerge <- function(list1,list2){
  names=union(names(list1),names(list2))
  print(names)
  finalList=list(names)
  for(i in 1:length(names)){
    finalList[[names[i]]]=rbind(list1[[names[i]]],list2[[names[i]]])
  }
  return(finalList)
}

min2sec=function(time){
  x=strsplit(time,":")
  if(length(x[[1]])==2){
    return(60*as.numeric(x[[1]][1])+as.numeric(x[[1]][2]))
  } else if(length(x[[1]])==1){
    return(as.numeric(x[[1]][1]))
  } else{
    return(60*60*as.numeric(x[[1]][1])+60*as.numeric(x[[1]][2])+as.numeric(x[[1]][3]))
  }
}

```


## Women's Indoor All Time Lists


```{r, echo=FALSE, warning=FALSE, include=FALSE}
url=c("https://www.tfrrs.org/all_performances/KY_college_f_Georgetown_KY.html?list_hnd=2330&season_hnd=429&printable=1&popup=1&width=800",
      "https://www.tfrrs.org/all_performances/KY_college_f_Georgetown_KY.html?list_hnd=2120&season_hnd=388&printable=1&popup=1&width=800",
      "https://www.tfrrs.org/all_performances/KY_college_f_Georgetown_KY.html?list_hnd=601&season_hnd=132&printable=1&popup=1&width=800",
      "https://www.tfrrs.org/all_performances/KY_college_f_Georgetown_KY.html?list_hnd=2776&season_hnd=474&printable=1&popup=1&width=800")

ITF2019=scrpTFRRS(url[1])
ITF2018=scrpTFRRS(url[2])
ITF2010=scrpTFRRS(url[3])
ITF2020=scrpTFRRS(url[4])

AllTimeList=listMerge(ITF2019,ITF2018)
AllTimeListFinal=listMerge(AllTimeList,ITF2010)
AllTimeListFinal=listMerge(AllTimeListFinal,ITF2020)
```

## 60 Meters

### All Time Performances

```{r echo=FALSE}

datatable(AllTimeListFinal[["60Meters"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'60Meters' %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## 200 Meters

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["200Meters"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```


### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'200Meters' %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## 400 Meters

### All Time Perfomaces

```{r echo=FALSE}
AllTimeListFinal$'400Meters'$TIME <- sapply(AllTimeListFinal$'400Meters'$TIME,min2sec)

datatable(AllTimeListFinal[["400Meters"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'400Meters' %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## 600 Meters

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["600Meters"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'600Meters' %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## 800 Meters

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["800Meters"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'800Meters' %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## 1000 Meters

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["1000Meters"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'1000Meters' %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```


## 1 Mile

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["Mile"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$Mile %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```


## 3000 Meters

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["3000Meters"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'3000Meters' %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```


## 5000 Meters

### All Time Performances

No Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["5000Meters"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

No Performances


## 60 Meter Hurdles

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["60Hurdles"]],rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'60Hurdles' %>% group_by(ATHLETE) %>% top_n(-1, TIME)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```


## 4x200m Relay

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["4x200Relay"]],rownames=FALSE,options = list(
  order = list(list(0, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```



## 4x400m Relay

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["4x400Relay"]],rownames=FALSE,options = list(
  order = list(list(0, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## DMR

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["DistanceMedleyRelay"]],rownames=FALSE,options = list(
  order = list(list(0, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```


## High Jump

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["HighJump"]],rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'HighJump' %>% group_by(ATHLETE) %>% top_n(1, MARK)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```


## Long Jump

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["LongJump"]],rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'LongJump' %>% group_by(ATHLETE) %>% top_n(1, MARK)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## Shot Put

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["ShotPut"]],rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```
### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'ShotPut' %>% group_by(ATHLETE) %>% top_n(1, MARK)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## Weight Throw

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["WeightThrow"]],rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'WeightThrow' %>% group_by(ATHLETE) %>% top_n(1, MARK)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

## 4x800m Relay

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["4x800Relay"]],rownames=FALSE,options = list(
  order = list(list(0, 'asc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```


## Pole Vault

### All Time Performances

```{r echo=FALSE}
datatable(AllTimeListFinal[["PoleVault"]],rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```

### Rankings

```{r echo=FALSE}


Rank <- AllTimeListFinal$'PoleVault' %>% group_by(ATHLETE) %>% top_n(1, MARK)

datatable(Rank,rownames=FALSE,options = list(
  order = list(list(2, 'desc')),
  pageLength = 5,
  lengthMenu = c(5,10, 15, 20, 25),
  searchHighlight = TRUE),
  filter = 'top')
```